### 2019-04-15 paper/paper.tex
expanded related works

Related research can be generally described as one of two types
of work: meta-analyses of the behaviour and importance
of software ecosystems, and empirical investigations into the
specifics of a particular ecosystem. Some topics 
for meta-analyses include ecosystem visualization \cite{LUNGU2010264},
ecosystem maturity \cite{Alves:2011}, quality metric aggregation \cite{Mordal:2013},
and literature reviews \cite{Manikas:2013, Manikas:2017}. Specific ecosystem analysis include works such as this
paper as well as the original research by Wittern, Suter and Rajagopalan \cite{Wittern:2016} on \code{npm}.
Others have performed evaluations of specific ecosystems such as Raemaekers et al. \cite{Raemaekers:2013},
who present a dataset with basic metrics, dependencies and changes within the popular 
Java-based Maven ecosystem. Another work investigates the
result of changing project interdependencies in Apache \cite{Bavota:2013}, 
and still others evaluate evolution over time in ecosystems like
Gentoo \cite{Bloemen:2014}, Ruby, \cite{Kabbedijk:2011}, and R \cite{Plakidas:2017}.

@@

>>>>

Related research can be generally described as one of two types
of work: meta-analyses of the behaviour and importance
of software ecosystems, and empirical investigations into the
specifics of a particular ecosystem. Some topics 
for meta-analyses include ecosystem visualization \cite{LUNGU2010264},
ecosystem maturity \cite{Alves:2011}, quality metric aggregation \cite{Mordal:2013},
and literature reviews \cite{Manikas:2013, Manikas:2017}. Specific ecosystem analysis include works such as this
paper as well as the original research by Wittern, Suter and Rajagopalan \cite{Wittern:2016} on \code{npm}.
Others have performed evaluations of specific ecosystems such as Raemaekers et al. \cite{Raemaekers:2013},
who present a dataset with basic metrics, dependencies and changes within the popular 
Java-based Maven ecosystem. Another work investigates the
result of changing project interdependencies in Apache \cite{Bavota:2013}, 
and still others evaluate evolution over time in ecosystems like
Gentoo \cite{Bloemen:2014}, Ruby, \cite{Kabbedijk:2011}, and R \cite{Plakidas:2017}.
Some works have looked empirically at the results of changing versions
within software ecosystems (including \code{npm}), finding that
developers often encounter difficulties when attempting to avoid
breaking dependencies \cite{Bogart:2015}.

Finally, \code{npm} has been investigated informally. In
the \code{pagerank} package, web-based \code{PageRanks} are used to evaluate
package popularity\footnote{https://www.npmjs.com/package/pagerank}.
The project code{npm-by-the-numbers} also provides various statistics
about the state of \code{npm}, but is significantly out of date and 
in contrast to this work does not provide an evaluation of the ecosystem over time
or give any insight into application usage\footnote{https://github.com/ashleygwilliams/npm-by-the-numbers}.

@@

  \bibitem{Bogart:2015}
  Christopher Bogart, Christian K{\"a}stner, and James Herbsleb.
  \newblock When it breaks, it breaks: How ecosystem developers reason about the
    stability of dependencies.
  \newblock In {\em Proceedings of the ASE Workshop on Software Support for
    Collaborative and Global Software Engineering (SCGSE)}, pages 86--89, 11
    2015.
